How to measure the radial velocity of a star

### 2022-07-24 paper/main.tex
doppler words; aastex

% to-do list
% ----------
% - Look for all instances of HOGG, BEDELL, and CITE.
% - Resolve all Overleaf (tm) comments.
% - Make an acronym command and fix CLRB, RV, and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Are we consistent in our use of Doppler shift, radial velocity, and redshift and so on? Fix figure captions so the figures are clearly in RV. Edit radial Doppler assumption section to say that the terms are interchangeable unless the star is moving relativistically (which it's not). cite Wright-group paper. Make it clear that for US, RV *is* the same as c * dx.
% - Do we address the relationship between our tiny spectral segment and a full spectrograph? Get scalings. Etc. Possibly we should ask Daunt to give us a realistic spectral segment?
% - Make sure we are explicit about what we are assuming that we know when we fit the CCF with a Gaussian.
% - Make sure all figures are explicitly referred to in the text.
% - Are we sensible in our use of first (and second?) person?
% - I believe we are inconsistent with the tense. Always present or always past? Decide and audit / fix. Probably present is better.
% - Cite Vakili et al for the parabola trick, maybe?
% - Comment on how to estimate RV uncertainties & the accuracy of those estimates for each technique?? Maybe we need a bootstrap / jackknife / multiple orders kind of discussion.
% - Fix all LaTeX warnings and errors.
% - Submit to arXiv.

@@

    We assume that all of these effects are negligible, and the Doppler shift of a given spectrum can be straightforwardly interpreted in terms of a single radial velocity.

@@

HOGG: What, roughly, is most important about the above?

>>>>

% to-do list
% ----------
% - Look for all instances of HOGG, BEDELL, and CITE.
% - Resolve all Overleaf (tm) comments.
% - Make an acronym command and fix CLRB, RV, and all other acronyms.
% - Be sure to discuss SNR in a continuum resolution element, as well as in a pixel.
%.- Make sure that, for any assumption that is explicitly tested, the forthcoming test is mentioned when the assumption is introduced.
% - Do we address the relationship between our tiny spectral segment and a full spectrograph? Get scalings. Etc. Possibly we should ask Daunt to give us a realistic spectral segment?
% - Make sure we are explicit about what we are assuming that we know when we fit the CCF with a Gaussian.
% - Make sure all figures are explicitly referred to in the text.
% - Are we sensible in our use of first (and second?) person?
% - I believe we are inconsistent with the tense. Always present or always past? Decide and audit / fix. Probably present is better.
% - Cite Vakili et al for the parabola trick, maybe?
% - Comment on how to estimate RV uncertainties & the accuracy of those estimates for each technique?? Maybe we need a bootstrap / jackknife / multiple orders kind of discussion.
% - Fix all LaTeX warnings and errors.
% - Submit to arXiv.

@@

    We assume that all of these effects are negligible, and the Doppler shift of a given spectrum can be straightforwardly interpreted in terms of a single radial velocity; thus for our purposes these terms (Doppler shift and radial velocity) can be used interchangeably.

@@

In this \documentname, we HOGG: What, roughly, is most important about the above?
